---
title: "STAT1601_Homework2"
author: "Kyndal Harrison"
date: "2/1/2020"
output: pdf_document
---

# Question 1
```{r}
library( ggplot2 )
RollerCoaster = read.csv("/Users/kyndalharrison/STAT1601/Class Materials/RollerCoasterData.csv")
with(RollerCoaster, table(State, Type))
```
Virginia has zero wooden Roller Coasters


# Question 2
```{r}
library( RColorBrewer)
ggplot( data = RollerCoaster, mapping = aes( x = Design))+ geom_bar( fill = brewer.pal( 7, "Set1"))+ theme( axis.text.x = element_text( angle = 90), plot.title = element_text( hjust = .5)) + labs( x = "Roller Coaster Design", y = "Number of Roller Coasters", title = "Roller Coasters")
```
This graph shows the amount of different designs of Roller Coasters.


# Question 3
```{r}
inversions = as.character(RollerCoaster$Inversions, na.rm = NULL)
ggplot( data = RollerCoaster, mapping = aes( x = Design, fill = inversions))+geom_bar( position = "stack")
```
This graph shows the amount of inversions per Roller Coaster design.

# Question 4
```{r}
ggplot( data = RollerCoaster, mapping = aes( x = age, fill = Type))+geom_histogram( binwidth = 10, bins = 10)

```
This graph depicts the relationship between age and a Roller Coaster being wooden or steel.


# Question 5
```{r}
ggplot( data = RollerCoaster, mapping = aes( x = State, y = age, fill = Type))+ geom_boxplot()+theme( axis.text.x = element_text( angle = 90))
```
This graph shows the deviation of the age of roller coasters per state and per type.


#Question 6
```{r}
ggplot( data = RollerCoaster, mapping = aes( x = Height, y = Speed, size = age))+geom_point( alpha = .35, aes( fill = Type, color = Type))
```
The graph shows the correlation of speed and height. It also shows which roller coasters are steel or wooden and how old they are by the size of the bubble.


#Question 7
```{r}
ggplot( data = RollerCoaster, mapping = aes( x = Inversions ))+ geom_bar(fill = brewer.pal( 8, "BuPu") )
```
The graph shows the amount of Roller Coasters with a certain amount of inversions.
